---
title: "Tetrapods - Zonation based on species, functional and food web link diversity"
author: 'Author: L Pollock'
date: 'Last update: "`r Sys.Date()`"'
output: pdf_document
---
  
This code plots biodiversity accumulation curves and priority maps for Zonation outputs
  

Zonation Runs:

Metawebs:
1. Adult-only interactions 'LinksAdult'
2. Interactions all life stages "LinksAll"

Biodiversity categories:
1. Species
2. Predator-prey food web links (see metawebs options)  
3. Stochastic Block Model Groups - Size 'GroupsSz'
4. Stochastic Block Model Groups - Probability 'GroupsPr'

Zonation optimization
1. Core Area 'CAZ'
2. Adtv Benefit Function 'ABF'

Land Tenure
1. Optimal - all of Europe considered
2. eu - protected areas mask




Step 1: summarize information for pixel-based removal from Zon files
```{r, eval=FALSE}

# functions page
source("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km/TetrapodFunctions.R")


setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km/ZonationOUT")

outputs <- gsub(".rank.compressed.tif","",list.files(pattern = "rank.compressed.tif"))

## subset to only runs for ENTIRE study area = 'optimal'
outputs <- outputs[ grep("optimal",outputs) ]

codes <- outputs

Tetra.Array <- run.curves.Tetrapods(outputs,codes) 

setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km")
#save(Tetra.Array,file='Tetrapods.Array.Rdata')


```





Step 2: plot biod. accumulation curves - how much different biod. metrics are captured for % area protected
```{r, eval=TRUE}


setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km")
source("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km/TetrapodFunctions.R")

load("Tetrapods.Array.Rdata")

cArray <- Tetra.Array


c1 <- "#878787"
c2 <- "#d6604d"
c3 <- "blue"

layrs <- c(dimnames(cArray)[[3]])

metrics <- c(dimnames(cArray)[[2]])



#fig 1 -------------------------------------------
setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km")

#pdf(file="FigCurves1.pdf",width=12,height=8)

par(mfrow=c(1,2))
par(mar=c(5,5,2,2))
cx <- 1.3

#1. species 
metrics <- rep("ScaledSumPropRichness",length(layrs))
colrs <- c(rep(c1,4),rep(c2,2),rep(c3,2))
linet <- c(rep(c(1,2),length(layrs)))

plot.curve.ov(cArray,layrs,metrics,colrs,linet,xlim=c(0,0.2),ylim=c(0,1.0))
axis(2,at = c(0.1,0.2,0.3,0.4,0.5,0.6,0.70,0.80,0.90,1.0),
       labels=c(10,20,30,40,50,60,70,80,90,100),las=1, col="black", ylab="",col.lab='black',col.axis='black',cex=1.7)
mtext("% Spatial Range Species Protected",side=2,col='black',padj=-3,cex=cx)

axis(1,at = c(.10,.20,.30,.40,.50,.60,.70,.80,.90,1),
     labels=c(10,20,30,40,50,60,70,80,90,100),las=1, col="black", ylab="",col.lab='black',col.axis='black',cex=1.7)
mtext("% Land Protected",side=1,col='black',padj=2.5,cex=cx)


legend("bottomright", # position
         legend = c("Groups","Links","Species"),
         lty = c(1,1),
         title = "",
         col = c(c1,c2,c3),
         text.col = c(c1,c2,c3),
         cex = 1,
         bty = "n") # border

#2. rare species  
metrics <- rep("ScaledSumPropRichnessRareSp",length(layrs))

plot.curve.ov(cArray,layrs,metrics,colrs,linet,xlim=c(0,0.2),ylim=c(0,1))
axis(2,at = c(0.1,0.2,0.3,0.4,0.5,0.6,0.70,0.80,0.90,1.0),
     labels=c(10,20,30,40,50,60,70,80,90,100),las=1, col="black", ylab="",col.lab='black',col.axis='black',cex=1.7)
mtext("% Spatial Range Rare Sp. Prot.",side=2,col='black',padj=-3,cex=cx)

axis(1,at = c(.10,.20,.30,.40,.50,.60,.70,.80,.90,1),
     labels=c(10,20,30,40,50,60,70,80,90,100),las=1, col="black", ylab="",col.lab='black',col.axis='black',cex=1.7)
mtext("% Land Protected",side=1,col='black',padj=2.5,cex=cx)

legend("bottomright", # position
       legend = c("Groups","Links","Species"),
       lty = c(1,1),
       title = "",
       col = c(c1,c2,c3),
       text.col = c(c1,c2,c3),
       cex = 1,
       bty = "n") # border

#dev.off()
#---------------------------------




```






Step 3: plot maps
```{r, eval=TRUE}

library(raster)
library(RColorBrewer)

setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km/ZonationOUT/")
outputs <- gsub(".rank.compressed.tif","",list.files(pattern = "rank.compressed.tif"))


# optimal maps
outputs <- outputs[grep('optimal',outputs)]

setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km/ZonationOUT/")

gr.pr.abf.opt <- raster("GroupsPrABFoptimal10km.rank.compressed.tif")
gr.pr.caz.opt <- raster("GroupsPrCAZoptimal10km.rank.compressed.tif")
gr.sz.abf.opt <- raster("GroupsSzABFoptimal10km.rank.compressed.tif")
gr.sz.caz.opt <- raster("GroupsSzCAZoptimal10km.rank.compressed.tif")
li.ad.caz.opt <- raster("LinksAdultCAZoptimal10km.rank.compressed.tif")
li.ad.abf.opt <- raster("LinksAdultABFoptimal10km.rank.compressed.tif")
sp.abf.opt <- raster("SpeciesABFoptimal10km.rank.compressed.tif")
sp.caz.opt <- raster("SpeciesCAZoptimal10km.rank.compressed.tif")



#set up gradient colors

# color brewer 6-class BuPu + one
c1 <- "#edf8fb"
c2 <- "#bfd3e6"
c3 <- "#9ebcda" 
c4 <- "#8c96c6"
c5 <- "#8856a7" 
c6 <- "#810f7c"
c7 <- "#4c0013" #hex monochromatic
#col.protected <- "#006d2c"


breakpoints <- c(0,0.25,0.50,0.75,0.90,0.95,0.99,1.0)
colz <- c(c1,c2,c3,c4,c5,c6,c7)


setwd("~/Documents/Manuscripts/EuropeanFoodWebCons/ConservationLinksPaper/Zonation10km/")

#png(filename = "TetraPriOptimalCAZ.png",width = 1200, height = 1200, units = "px")
#caz
par(mfrow=c(2,2))
par(mar=c(.01,.01,.01,.01))
plot(sp.caz.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='Species')
plot(li.ad.caz.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='LinksAdult')
plot(gr.pr.caz.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='GroupsPr')
plot(gr.sz.caz.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='GroupsSz')
#dev.off()


#png(filename = "TetraPriOptimalABF.png",width = 1200, height = 1200, units = "px")
#abf
par(mfrow=c(2,2))
par(mar=c(.01,.01,.01,.01))
plot(sp.abf.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='Species')
plot(gr.pr.abf.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='GroupsPr')
plot(gr.sz.abf.opt,breaks=breakpoints,col=colz,axes=F,legend=F,box=F,main='GroupsSz')
plot(1,1,col='white')
legend("bottomright",inset=c(0,0), # position
       legend = c("0-25", "25-50", "50-75","75-90","90-95","95-99","99-100","Protected"), 
       title = "",
       fill = colz,
       cex = 1.5,
       bty = "n") # border

#ev.off()



#png(filename = "DiffMaps.png",width = 1200, height = 600, units = "px")

par(mfrow=c(1,2))
diff <- li.ad.caz.opt - sp.caz.opt
colors <- c( colorRampPalette(brewer.pal(8,'PuOr'))(8))

breakpoints <- c(-1,-0.5,-0.2,-0.1,0,0.1,0.2,0.5,1)
plot(diff,breaks=breakpoints,col=colors,axes=F,box=F,legend=T,main="Links minus species")

diff <- gr.pr.caz.opt - sp.caz.opt
plot(diff,breaks=breakpoints,col=colors,axes=F,box=F,legend=T,main="Groups minus species")
#dev.off()         






```
